GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring

### 2020-12-13 paper/manuscript-iot.tex
submit to supervisor
add poofeading 2.0

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{GNSS-based displacement detection using Bayesian inference for deformation monitoring}
	%
	%
	% author names and IEEE memberships
	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
	% a structure at a ~ so this keeps an author's name from being broken across
	% two lines.
	% use \thanks{} to gain access to the first footnote area
	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
	% was not built to handle multiple paragraphs
	%

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison. 
	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

\subsubsection{State Model}
The state model is defined as follows (Takasu 2013)
\begin{equation}
{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
\end{equation}
where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; 
Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
\subsubsection{Extended Kalman filtering}
Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
\begin{equation}
{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
\end{equation}
\begin{equation}
{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
\end{equation}
According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged. However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged. The measurement update process is as follows:
\begin{equation}
{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
\end{equation}
\begin{equation}
{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
\end{equation}
\begin{equation}
{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
\end{equation}
where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix. The final state is estimated as follows:
\begin{equation}
{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
\end{equation}
\begin{equation}
{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
\end{equation}
where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.

>>>>

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring}
	%
	%
	% author names and IEEE memberships
	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
	% a structure at a ~ so this keeps an author's name from being broken across
	% two lines.
	% use \thanks{} to gain access to the first footnote area
	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
	% was not built to handle multiple paragraphs
	%

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	In order to evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7mm and 7.9mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

@@

\subsubsection{State Model}
The state model is defined as follows (Takasu 2013)
\begin{equation}
{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
\end{equation}
where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; 
Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
\subsubsection{Extended Kalman filtering}
Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
\begin{equation}
{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
\end{equation}
\begin{equation}
{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
\end{equation}
where ${\bf{\hat x}}_{k|k - 1}$ is the predicted value and ${\bf{Q}}_{k|k - 1}$ is the corresponding covariance. According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged. However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged. The measurement update process is as follows:
\begin{equation}
{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
\end{equation}
\begin{equation}
{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
\end{equation}
\begin{equation}
{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
\end{equation}
where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix. The final state is estimated as follows:
\begin{equation}
{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
\end{equation}
\begin{equation}
{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
\end{equation}
where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the Bayesian inference.
